Usage metrics

### 2021-03-08 analysis/usage.Rmd
Fix problems with notebook generation per dataset

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/kaggle/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

dataset_name <- basename(params$base_dir)
create_tags(path(TAGS_DIR, paste0(dataset_name, "_usage_metrics.tex")), prefix = dataset_name, default = TRUE)

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

dataset_name <- basename(params$base_dir)
create_tags(path(TAGS_DIR, paste0(dataset_name, "_usage_metrics.tex")), prefix = dataset_name, default = TRUE)
#create_tags(path(TAGS_DIR, "usage_metrics.tex"), default = TRUE)
